My title

### 2024-11-03 paper/paper.qmd
Update paper.qmd
Update graphs in data

# Create the table using kable
kable(variable_descriptions) %>%
  kable_styling() %>%
  column_spec(1, width = "4.5cm") %>% # Adjust the width of the first column
  column_spec(2, width = "10cm")    # Adjust the width of the second column
```
52个varibles中以下几个与我们的project明显无关，我们在此不做讨论：
"notes", "url", "url_article", "url_topline", "url_crosstab", "source"
```{r, fig.height=90, fig.width=90}
#| warning: false
#| message: false
#| echo: false
del_1 <- c("notes", "url", "url_article", "url_topline", "url_crosstab", "source")
droped_data <- raw_data %>% select(-any_of(del_1))
```
此外，还有一些相同的variables，我们保留其一，剩下的也不做讨论，它们包括："pollster", "sponsors", "display_name", "pollster_rating_name", "sponsor_candidate", "endorsed_candidate_name", "population_full", "candidate_id", "candidate_name"
```{r}
#| warning: false
#| message: false
#| echo: false
# 这里需要画一个table，展示删除的重复变量
del_2 <- c("pollster", "sponsors", "display_name", "pollster_rating_name", "sponsor_candidate", "endorsed_candidate_name",
           "population_full", "candidate_id", "candidate_name")
droped_data <- droped_data %>% select(-any_of(del_2))
```
常数变量我们也不做讨论，因为无法影响我们的预测，它们是：
```{r, fig.height=90, fig.width=90}
#| warning: false
#| message: false
#| echo: false
#| label: tbl-cv
#| tbl-cap: "Constant variables"
# Identify variables where all values are the same (including NA)
same_value_variables <- names(droped_data)[sapply(droped_data, function(x) length(unique(x)) == 1)]
# Create a data frame with variables and their unique values
same_value_data <- data.frame(Variable = same_value_variables, Value = sapply(same_value_variables, function(var)
unique(na.omit(droped_data[[var]]))[1]))
# Print the names of variables with all identical values using kable
kable(same_value_data[, 2, drop = FALSE], col.names = c("Variable", "Value"))
del_4 <- c("endorsed_candidate_id", "endorsed_candidate_party", "subpopulation", "cycle", "election_date", "stage", "nationwide_batch", 
           "office_type", "seat_number", "seat_name")
droped_data <- droped_data %>% select(-any_of(del_4))
```
其中categorical的有"poll_id", "pollster_id", "sponsor_ids", "pollster_rating_id", "methodology", "state",
         "sponsor_candidate_id", "sponsor_candidate_party", "question_id", "population", "tracking", "created_at", "internal",
         "partisan","race_id", "ranked_choice_reallocated", "ranked_choice_round", "hypothetical","party","answer"
```{r}
#| warning: false
#| message: false
#| echo: false
catego <- c("poll_id", "pollster_id", "sponsor_ids", "pollster_rating_id", "methodology", "state",
         "sponsor_candidate_id", "sponsor_candidate_party", "question_id", "population", "tracking", "created_at", "internal",
         "partisan","race_id", "ranked_choice_reallocated", "ranked_choice_round", "hypothetical","party","answer")
```
重要的categorical为下面的，剩下的将在appendix阐述："poll_id", "methodology", "population", "ranked_choice_reallocated", "hypothetical","answer"
```{r}
#| warning: false
#| message: false
#| echo: false
catego_inp <- c("poll_id", "methodology", "population", "ranked_choice_reallocated", "hypothetical","answer")
```
一共有3530个poll
```{r}
#| warning: false
#| message: false
#| echo: false
# Get unique Poll IDs and print the count
unique_poll_ids <- unique(raw_data$poll_id)
```
描述
```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-bv
#| fig-cap: "Boolean variables"
plots <- list()
# Create bar charts for 'ranked_choice_reallocated' and 'hypothetical'
plots[["ranked_choice"]] <- ggplot(raw_data, aes(x = ranked_choice_reallocated)) +
  geom_bar(fill = "#69b3a2", color = "black", alpha = 0.8) +
  labs(title = "Ranked Choice Reallocated", x = "Ranked Choice Reallocated", y = "Count") +
  theme_minimal(base_size = 15) +
  theme(
    plot.title = element_text(hjust = 0.5, size = 12),
    axis.title = element_text(size = 10),
    axis.text = element_text(size = 10)
  )

plots[["hypothetical"]] <- ggplot(raw_data, aes(x = hypothetical)) +
  geom_bar(fill = "#69b3a2", color = "black", alpha = 0.8) +
  labs(title = "Hypothetical", x = "Hypothetical", y = "Count") +
  theme_minimal(base_size = 15) +
  theme(
    plot.title = element_text(hjust = 0.5, size = 12),
    axis.title = element_text(size = 10),
    axis.text = element_text(size = 10)
  )

# Combine and print the plots using patchwork
combined_plot <- wrap_plots(plots, ncol = 2, nrow = 1, heights = unit(rep(3, 4), "in")) +
  plot_annotation(
    theme = theme(
      plot.title = element_text(hjust = 0.5, size = 14)
    )
  )
# Print the combined plot
print(combined_plot)

@@

plots <- list()
# Find the top 3 most frequent values in 'methodology' and group others as 'Other'
methodology_counts <- sort(table(raw_data$methodology), decreasing = TRUE)
top_3_methodologies <- names(methodology_counts)[1:3]
raw_data$methodology_grouped <- ifelse(raw_data$methodology %in% top_3_methodologies, raw_data$methodology, "Other")
# Create a bar chart for the grouped 'methodology'
plots[["methodology"]] <- ggplot(raw_data, aes(x = methodology_grouped)) +
  geom_bar(fill = "#69b3a2", color = "black", alpha = 0.8) +
  labs(title = "Top 3 Methodologies and Others", x = "Methodology", y = "Count") +
  theme_minimal(base_size = 15) +
  theme(
    plot.title = element_text(hjust = 0.5, size = 12),
    axis.title = element_text(size = 10),
    axis.text = element_text(size = 10)
  )
plots[["population"]] <- ggplot(raw_data, aes(x = population)) +
  geom_bar(fill = "#69b3a2", color = "black", alpha = 0.8) +
  labs(title = "Population", x = "Population", y = "Count") +
  theme_minimal(base_size = 15) +
  theme(
    plot.title = element_text(hjust = 0.5, size = 12),
    axis.title = element_text(size = 10),
    axis.text = element_text(size = 10)
  )
# Find the top 3 most frequent values in 'answer' and group others as 'Other'
answer_counts <- sort(table(raw_data$answer), decreasing = TRUE)
top_3_answer <- names(answer_counts)[1:3]
raw_data$answer <- ifelse(raw_data$answer %in% top_3_answer, raw_data$answer, "Other")
# Create a bar chart for the grouped 'answer'
plots[["answer"]] <- ggplot(raw_data, aes(x = answer)) +
  geom_bar(fill = "#69b3a2", color = "black", alpha = 0.8) +
  labs(title = "Top 3 answer and Others", x = "answer", y = "Count") +
  theme_minimal(base_size = 15) +
  theme(
    plot.title = element_text(hjust = 0.5, size = 12),
    axis.title = element_text(size = 10),
    axis.text = element_text(size = 10)
  )
combined_plot <- wrap_plots(plots, ncol = 3, nrow = 1, heights = unit(rep(8, 4), "in")) +
  plot_annotation(
    theme = theme(
      plot.title = element_text(hjust = 0.5, size = 14)
    )
  )
# Print the combined plot
print(combined_plot)
以及numerical的variables："numeric_grade"      "pollscore"          "transparency_score" "start_date"         "end_date"        "sample_size" "pct"
#| warning: false
#| message: false
#| echo: false
numer <- droped_data %>% select(-any_of(catego))
描述
```{r, fig.pos="H", fig.width=18, fig.height=18}
#| warning: false
#| message: false
#| echo: false
#| label: fig-donvp1
#| fig-cap: "Distribution of numerical varibales part 1"
### Create Plots for Numeric Variables ###
# Create a list to store plots
plots <- list()
# Loop through selected numeric variables and plot their distributions
for (variable in names(numer %>% select(numeric_grade, pollscore, transparency_score))) {
  plots[[variable]] <- ggplot(raw_data, aes_string(x = variable)) +
    geom_histogram(binwidth = 0.5, fill = "#69b3a2", color = "black", alpha = 0.8) +
    labs(title = paste("Distribution of", variable), x = variable, y = "Frequency") +
    theme_minimal(base_size = 30) +
    theme(
      plot.title = element_text(hjust = 0.5, size = 12),
      axis.title = element_text(size = 20),
      axis.text = element_text(size = 20)
    )
}
### Combine and Print Plots ###
# Combine all individual plots into one using patchwork with 2 columns and 4 rows
combined_plot <- wrap_plots(plots, ncol = 3, nrow = 1, heights = unit(rep(8, 4), "in")) +
  plot_annotation(
    theme = theme(
      plot.title = element_text(hjust = 0.5, size = 14)
    )
  )
# Print the combined plot
print(combined_plot)
描述
```{r, fig.pos="H", fig.width=18, fig.height=18}
#| warning: false
#| message: false
#| echo: false
#| label: fig-donvp2
#| fig-cap: "Distribution of numerical varibales part 2"
### Create Plots for Numeric Variables ###
# Create a list to store plots
plots <- list()
# Loop through selected numeric variables and plot their distributions
for (variable in names(numer %>% select(sample_size, pct))) {
  plots[[variable]] <- ggplot(raw_data, aes_string(x = variable)) +
    geom_histogram(binwidth = 5, fill = "#69b3a2", color = "black", alpha = 0.8) +
    labs(title = paste("Distribution of", variable), x = variable, y = "Frequency") +
    theme_minimal(base_size = 30) +
    theme(
      plot.title = element_text(hjust = 0.5, size = 12),
      axis.title = element_text(size = 10),
      axis.text = element_text(size = 10)
    )
}
### Combine and Print Plots ###
# Combine all individual plots into one using patchwork with 2 columns and 4 rows
combined_plot <- wrap_plots(plots, ncol = 2, nrow = 1, heights = unit(rep(8, 8), "in")) +
  plot_annotation(
    theme = theme(
      plot.title = element_text(hjust = 0.5, size = 14)
    )
  )
# Print the combined plot
print(combined_plot)
描述
```{r, fig.pos="H", fig.width=18, fig.height=18}
#| warning: false
#| message: false
#| echo: false
#| label: fig-dodv
#| fig-cap: "Distribution of date varibales"

### Define Variables and Prepare Data ###
# Convert start_date and end_date to Date type
raw_data$start_date <- ymd(raw_data$start_date)
raw_data$end_date <- ymd(raw_data$end_date)
# Define the date variables to plot
date_variables <- c("start_date", "end_date")
### Create Plots for Date Variables ###
# Loop through selected date variables and plot their distributions
plots <- list()
for (variable in names(numer %>% select(start_date, end_date))) {
  plots[[variable]] <- ggplot(raw_data, aes_string(x = variable)) +
    geom_histogram(binwidth = 80, fill = "#69b3a2", color = "black", alpha = 0.8) +
    labs(title = paste("Distribution of", variable), x = variable, y = "Frequency") +
        theme_minimal(base_size = 30) +
    theme(
      plot.title = element_text(hjust = 0.5, size = 12),
      axis.title = element_text(size = 10),
      axis.text = element_text(size = 10)
    )
}
### Combine and Print Plots ###
# Combine all individual plots into one using patchwork with 2 columns and 4 rows
combined_plot <- wrap_plots(plots, ncol = 2, nrow = 1, heights = unit(rep(8, 4), "in")) +
  plot_annotation(
    theme = theme(
      plot.title = element_text(hjust = 0.5, size = 14)
    )
  )
# Print the combined plot
print(combined_plot)

>>>>

# Create the table using kable
kable(variable_descriptions) %>%
  kable_styling() %>%
  column_spec(1, width = "4.5cm") %>% # Adjust the width of the first column
  column_spec(2, width = "10cm")    # Adjust the width of the second column
```
52个varibles中以下几个与我们的project明显无关，我们在此不做讨论：
"notes", "url", "url_article", "url_topline", "url_crosstab", "source"
```{r, fig.height=90, fig.width=90}
#| warning: false
#| message: false
#| echo: false
del_1 <- c("notes", "url", "url_article", "url_topline", "url_crosstab", "source")
droped_data <- raw_data %>% select(-any_of(del_1))
```
此外，还有一些相同的variables，我们保留其一，剩下的也不做讨论，它们包括："pollster", "sponsors", "display_name", "pollster_rating_name", "sponsor_candidate", "endorsed_candidate_name", "population_full", "candidate_id", "candidate_name"
```{r}
#| warning: false
#| message: false
#| echo: false
# 这里需要画一个table，展示删除的重复变量
del_2 <- c("pollster", "sponsors", "display_name", "pollster_rating_name", "sponsor_candidate", "endorsed_candidate_name",
           "population_full", "candidate_id", "candidate_name")
droped_data <- droped_data %>% select(-any_of(del_2))
```
常数变量我们也不做讨论，因为无法影响我们的预测，它们是：
```{r, fig.height=90, fig.width=90}
#| warning: false
#| message: false
#| echo: false
#| label: tbl-cv
#| tbl-cap: "Constant variables"
# Identify variables where all values are the same (including NA)
same_value_variables <- names(droped_data)[sapply(droped_data, function(x) length(unique(x)) == 1)]
# Create a data frame with variables and their unique values
same_value_data <- data.frame(Variable = same_value_variables, Value = sapply(same_value_variables, function(var)
unique(na.omit(droped_data[[var]]))[1]))
# Print the names of variables with all identical values using kable
kable(same_value_data[, 2, drop = FALSE], col.names = c("Variable", "Value"))
del_4 <- c("endorsed_candidate_id", "endorsed_candidate_party", "subpopulation", "cycle", "election_date", "stage", "nationwide_batch", 
           "office_type", "seat_number", "seat_name")
droped_data <- droped_data %>% select(-any_of(del_4))
```
其中categorical的有"poll_id", "pollster_id", "sponsor_ids", "pollster_rating_id", "methodology", "state",
         "sponsor_candidate_id", "sponsor_candidate_party", "question_id", "population", "tracking", "created_at", "internal",
         "partisan","race_id", "ranked_choice_reallocated", "ranked_choice_round", "hypothetical","party","answer"
```{r}
#| warning: false
#| message: false
#| echo: false
catego <- c("poll_id", "pollster_id", "sponsor_ids", "pollster_rating_id", "methodology", "state",
         "sponsor_candidate_id", "sponsor_candidate_party", "question_id", "population", "tracking", "created_at", "internal",
         "partisan","race_id", "ranked_choice_reallocated", "ranked_choice_round", "hypothetical","party","answer")
```
重要的categorical为下面的，剩下的将在appendix阐述："poll_id", "methodology", "population", "ranked_choice_reallocated", "hypothetical","answer"
```{r}
#| warning: false
#| message: false
#| echo: false
catego_inp <- c("poll_id", "methodology", "population", "ranked_choice_reallocated", "hypothetical","answer")
```
一共有3530个poll
```{r}
#| warning: false
#| message: false
#| echo: false
# Get unique Poll IDs and print the count
unique_poll_ids <- unique(raw_data$poll_id)
```
描述
```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-bv
#| fig-cap: "Boolean variables"

# Create a list to store the plots
plots <- list()

# Bar chart for 'ranked_choice_reallocated' with count labels
plots[["ranked_choice"]] <- ggplot(raw_data, aes(x = ranked_choice_reallocated)) +
  geom_bar(fill = "#69b3a2", color = "black", alpha = 0.8) +
  geom_text(stat = "count", aes(label = after_stat(count)), vjust = -0.5, size = 4) +  # Updated count label notation
  labs(title = "Bar Chart of Ranked Choice Reallocated", x = "Ranked Choice Reallocated", y = "Count") +
  theme_minimal(base_size = 15) +
  theme(
    plot.title = element_text(hjust = 0.5, size = 12),
    axis.title = element_text(size = 10),
    axis.text = element_text(size = 10)
  ) +
  ylim(0, max(table(raw_data$ranked_choice_reallocated)) * 1.2)  # Increase y-axis limit to fit labels

# Bar chart for 'hypothetical' with count labels
plots[["hypothetical"]] <- ggplot(raw_data, aes(x = hypothetical)) +
  geom_bar(fill = "#69b3a2", color = "black", alpha = 0.8) +
  geom_text(stat = "count", aes(label = after_stat(count)), vjust = -0.5, size = 4) +  # Updated count label notation
  labs(title = "Bar Chart of Hypothetical", x = "Hypothetical", y = "Count") +
  theme_minimal(base_size = 15) +
  theme(
    plot.title = element_text(hjust = 0.5, size = 12),
    axis.title = element_text(size = 10),
    axis.text = element_text(size = 10)
  ) +
  ylim(0, max(table(raw_data$hypothetical)) * 1.2)  # Increase y-axis limit to fit labels

# Combine and print the plots using patchwork
combined_plot <- wrap_plots(plots, ncol = 2) +
  plot_annotation(
    theme = theme(
      plot.title = element_text(hjust = 0.5, size = 14)
    )
  )

# Print the combined plot
print(combined_plot)

@@

# Create a list to store the plots
plots <- list()

# Top 3 Methodologies with 'Other' grouped
methodology_counts <- sort(table(raw_data$methodology), decreasing = TRUE)
top_3_methodologies <- names(methodology_counts)[1:3]
raw_data$methodology_grouped <- ifelse(raw_data$methodology %in% top_3_methodologies, raw_data$methodology, "Other")

# Create horizontal bar chart for 'methodology'
plots[["methodology"]] <- ggplot(raw_data, aes(x = methodology_grouped)) +
  geom_bar(fill = "#69b3a2", color = "black", alpha = 0.8) +
  geom_text(stat = "count", aes(label = after_stat(count)), hjust = -0.2, size = 9) +  # Larger count labels
  labs(title = "Top 3 Methodologies and Others", x = "Count", y = "Methodology") +
  theme_minimal(base_size = 24) +  # Increase base size for all text elements
  theme(
    plot.title = element_text(hjust = 0.5, size = 32, face = "bold"),  # Title font size
    axis.title = element_text(size = 28),  # Axis title font size
    axis.text = element_text(size = 24)  # Axis text font size
  ) +
  coord_flip()

# Population bar chart
plots[["population"]] <- ggplot(raw_data, aes(x = population)) +
  geom_bar(fill = "#69b3a2", color = "black", alpha = 0.8) +
  geom_text(stat = "count", aes(label = after_stat(count)), hjust = -0.2, size = 9) +  # Larger count labels
  labs(title = "Population", x = "Count", y = "Population") +
  theme_minimal(base_size = 24) +  # Increase base size for all text elements
  theme(
    plot.title = element_text(hjust = 0.5, size = 32, face = "bold"),  # Title font size
    axis.title = element_text(size = 28),  # Axis title font size
    axis.text = element_text(size = 24)  # Axis text font size
  ) +
  coord_flip()

# Top 3 Answers with 'Other' grouped
answer_counts <- sort(table(raw_data$answer), decreasing = TRUE)
top_3_answer <- names(answer_counts)[1:3]
raw_data$answer <- ifelse(raw_data$answer %in% top_3_answer, raw_data$answer, "Other")

# Create horizontal bar chart for 'answer'
plots[["answer"]] <- ggplot(raw_data, aes(x = answer)) +
  geom_bar(fill = "#69b3a2", color = "black", alpha = 0.8) +
  geom_text(stat = "count", aes(label = after_stat(count)), hjust = -0.2, size = 9) +  # Larger count labels
  labs(title = "Top 3 Answers and Others", x = "Count", y = "Answer") +
  theme_minimal(base_size = 24) +  # Increase base size for all text elements
  theme(
    plot.title = element_text(hjust = 0.5, size = 32, face = "bold"),  # Title font size
    axis.title = element_text(size = 28),  # Axis title font size
    axis.text = element_text(size = 24)  # Axis text font size
  ) +
  coord_flip()

# Combine the plots using patchwork
combined_plot <- wrap_plots(plots, ncol = 1) +
  plot_annotation(
    theme = theme(
      plot.title = element_text(hjust = 0.5, size = 32)
    )
  )

# Print the combined plot
print(combined_plot)

```
描述
```{r, fig.pos="H", fig.width=18, fig.height=18}
#| warning: false
#| message: false
#| echo: false
#| label: fig-donvp1
#| fig-cap: "Distribution of numerical varibales part 1"

### Create Plots for Numeric Variables ###
# Create a list to store plots
plots <- list()

# Loop through selected numeric variables and plot their distributions with a line connecting bar tops
for (variable in names(numer %>% select(numeric_grade, pollscore, transparency_score))) {
  # Calculate bin counts and midpoints
  bin_data <- ggplot_build(
    ggplot(raw_data, aes_string(x = variable)) +
      geom_histogram(binwidth = 0.5)
  )$data[[1]]

  # Calculate the midpoint of each bin for line plotting
  bin_data <- bin_data %>%
    mutate(midpoint = (xmin + xmax) / 2)

  # Create histogram plot with line connecting the bar tops
  plots[[variable]] <- ggplot(raw_data, aes_string(x = variable)) +
    geom_histogram(binwidth = 0.5, fill = "#69b3a2", color = "black", alpha = 0.8) +
    labs(title = paste("Distribution of", variable), x = variable, y = "Frequency") +
    theme_minimal(base_size = 24) +  # Adjusted base font size for readability
    theme(
      plot.title = element_text(hjust = 0.5, size = 35, face = "bold"),  # Larger title font size
      axis.title = element_text(size = 35),  # Axis title font size
      axis.text = element_text(size = 35)  # Axis text font size
    )
}

### Combine and Print Plots ###
# Combine all individual plots into one vertical layout
combined_plot <- wrap_plots(plots, ncol = 1) +
  plot_annotation(
    theme = theme(
      plot.title = element_text(hjust = 0.5, size = 35)
    )
  )

# Print the combined plot
print(combined_plot)

```
描述
```{r, fig.pos="H", fig.width=18, fig.height=18}
#| warning: false
#| message: false
#| echo: false
#| label: fig-donvp2
#| fig-cap: "Distribution of numerical varibales part 2"

### Create Plots for Numeric Variables ###
# Create a list to store plots
plots <- list()

# Loop through selected numeric variables and plot their distributions
for (variable in names(numer %>% select(sample_size, pct))) {
  if (variable == "sample_size") {
    # For sample_size, focus on the range 0-20000
    plots[[variable]] <- ggplot(raw_data, aes_string(x = variable)) +
      geom_histogram(binwidth = 500, fill = "#69b3a2", color = "black", alpha = 0.8) +
      xlim(0, 10000) +  # Set x-axis limits to focus on 0-10000 range
      labs(title = "Distribution of Sample Size (0-10000)", x = variable, y = "Frequency") +
      theme_minimal(base_size = 24) +
      theme(
        plot.title = element_text(hjust = 0.5, size = 35, face = "bold"),  # Larger title font size
        axis.title = element_text(size = 30),  # Larger axis title font size
        axis.text = element_text(size = 28)  # Larger axis text font size
      )
  } else {
    # For other variables, keep the full range
    plots[[variable]] <- ggplot(raw_data, aes_string(x = variable)) +
      geom_histogram(binwidth = 5, fill = "#69b3a2", color = "black", alpha = 0.8) +
      labs(title = paste("Distribution of", variable), x = variable, y = "Frequency") +
      theme_minimal(base_size = 24) +
      theme(
        plot.title = element_text(hjust = 0.5, size = 35, face = "bold"),  # Larger title font size
        axis.title = element_text(size = 30),  # Larger axis title font size
        axis.text = element_text(size = 28)  # Larger axis text font size
      )
  }
}

### Combine and Print Plots ###
# Combine all individual plots into one vertical layout
combined_plot <- wrap_plots(plots, ncol = 1) +
  plot_annotation(
    theme = theme(
      plot.title = element_text(hjust = 0.5, size = 35)
    )
  )

# Print the combined plot
print(combined_plot)

```
描述
```{r, fig.pos="H", fig.width=18, fig.height=18}
#| warning: false
#| message: false
#| echo: false
#| label: fig-dodv
#| fig-cap: "Distribution of date varibales"

### Define Variables and Prepare Data ###
# Convert start_date and end_date to Date type
raw_data$start_date <- ymd(raw_data$start_date)
raw_data$end_date <- ymd(raw_data$end_date)

# Define the date variables to plot
date_variables <- c("start_date", "end_date")

### Create Plots for Date Variables ###
# Create a list to store plots
plots <- list()

# Loop through selected date variables and plot their distributions with a density curve
for (variable in date_variables) {
  plots[[variable]] <- ggplot(raw_data, aes_string(x = variable)) +
    geom_histogram(fill = "#69b3a2", color = "black", alpha = 0.8) +  # Keep the original binwidth
    labs(title = paste("Distribution of", variable), x = variable, y = "Frequency") +
    theme_minimal(base_size = 24) +
    theme(
      plot.title = element_text(hjust = 0.5, size = 35, face = "bold"),  # Larger title font size
      axis.title = element_text(size = 30),  # Larger axis title font size
      axis.text = element_text(size = 28)  # Larger axis text font size
    )
}

### Combine and Print Plots ###
# Arrange the plots vertically without changing their individual orientation
combined_plot <- wrap_plots(plots, ncol = 1) +
  plot_annotation(
    theme = theme(
      plot.title = element_text(hjust = 0.5, size = 35)
    )
  )

# Print the combined plot
print(combined_plot)
